
sunburstr {data-navmenu="Packages"}
========================================


Column {.tabset}
--------------


### Load the {sunburstr} Package 

```{r }
library(sunburstR)
packageVersion("sunburstR")
#> [1] '2.1.6'

library(htmltools)
library(d3r)

#Simple data should suffice for these examples.

```

### Simple Data Set

```{r}


dat <- data.frame(
  level1 = rep(c("a", "b"), each=3),
  level2 = paste0(rep(c("a", "b"), each=3), 1:3),
  size = c(10,5,2,3,8,6),
  stringsAsFactors = FALSE
)

```


```{r}
knitr::kable(dat)



```


### d3r

d3r will help us build our hierarchy.

```{r}
library(d3r)
tree <- d3_nest(dat, value_cols = "size")
tree


```

Often the legend in the sunburst becomes useless with lots of nodes and multiple levels. 
While a hack could turn it off, I don't like having to ask users to resort to hacks, so now the argument legend = FALSE will turn it off.

```{r}
legend = FALSE


```


### output


```{r}
sb1 <- sunburst(
  tree, 
  width="100%", 
  height=400
)
sb1

```



### removed legend

```{r}
sb2 <- sunburst(
  tree,
  legend = FALSE,
  width = "100%",
  height = 400
)

sb2

```

### Comparison

<pre><code>

# do side-by-side for comparison

div(
  style="display: flex; align-items:center;",
  div(style="width:50%; border:1px solid #ccc;", sb1),
  div(style="width:50%; border:1px solid #ccc;", sb2)
)

</code><pre>

