---
title: "Likert Plots"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Likert 
========================================================





```{r}

require(ggplot2)
 
## generate fake likert data
set.seed(200)
response_scale <- c("Strongly Disagree",
                    "Disagree",
                    "Neither Agree or Disagree",
                    "Agree", 
                    "Strongly Agree")
x <- replicate(5, ordered(sample(response_scale, 20, replace = TRUE),
                          levels = response_scale), simplify = F)
x <- as.data.frame(x)
names(x) <- paste0("Q", 1:5)
 
## plot it as net stacked distribution
net_stacked(x)


```


```{r}
library(ggplot2)
library(reshape2)
library(RColorBrewer)
library(likert)
choices  = c("Very low", "Low", "Rather low", "Neither low nor high", "Rather high", "High", "Very high")
for(i in 1:ncol(items)) {
  items[,i] = factor(items[,i], levels=1:7, labels=choices, ordered=TRUE)
}
plot(likert(items), ordered=FALSE)
```
```{r}
# create summary table
table_summary = likert(items)
# reshape results
results = melt(table_summary$results, id.vars='Item')
# reorder results
results$Item = factor(results$Item, levels=c("LT", "ST", "SemTag", "SemTagContext"))
# some defaults
ymin = 0
text.size = 3
```

```{r fig.width=7, fig.height=6}
ggplot(results, aes(y=value, x=Item, group=Item)) + 
  geom_bar(stat='identity', aes(fill=variable)) + 
  ylim(c(-5,105)) + 
  coord_flip() +
  scale_fill_manual('Response', values=brewer.pal(7, "RdYlGn"), 
              breaks=levels(results$variable), 
              labels=levels(results$variable)) +
  geom_text(data=table_summary$summary, y=ymin, aes(x=Item, 
              label=paste(round(low), '%', sep='')), 
              size=text.size, hjust=1) +
  geom_text(data=table_summary$summary, y=100, aes(x=Item,
              label=paste(round(high), '%', sep='')), 
              size=text.size, hjust=-.2) +
  ylab('Percentage') + xlab('')
```




# http://stackoverflow.com/questions/14415674/reordering-groups-in-likert-plots-with-r
# additional requirements

library(ggplot2)
library(reshape2)
library(RColorBrewer)

# create summary table
table_summary = likert(items)

# reshape results
results = melt(table_summary$results, id.vars='Item')

# reorder results
results$Item = factor(results$Item, levels=c("LT", "ST", "SemTag", "SemTagContext"))

# some defaults
ymin = 0
text.size = 3

##############################################################

ggplot(results, aes(y=value, x=Item, group=Item)) + 
  geom_bar(stat='identity', aes(fill=variable)) + 
  ylim(c(-5,105)) + 
  coord_flip() +
  scale_fill_manual('Response', values=brewer.pal(7, "RdYlGn"), 
              breaks=levels(results$variable), 
              labels=levels(results$variable)) +
  geom_text(data=table_summary$summary, y=ymin, aes(x=Item, 
              label=paste(round(low), '%', sep='')), 
              size=text.size, hjust=1) +
  geom_text(data=table_summary$summary, y=100, aes(x=Item,
              label=paste(round(high), '%', sep='')), 
              size=text.size, hjust=-.2) +
  ylab('Percentage') + xlab('')
  
  