---
title: "``autoplot.density``Autoplot stats::density"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggfortify)
```


as_tibble.basis
as_tibble.basis
Convert a spline basis to a tibble

#### Description 
 
Convert a spline basis to a tibble

#### Usage 
<pre><code>
## S3 method for class 'basis'
as_tibble(x, ...)
</code></pre>

#### Arguments 
 
x object of class "basis"
... Ignored.

#### Details
This function is needed because the default method for converting a matrix object with an additional class attribute to a tibble causes issues because each column of the resulting tibble has the attributes, including the matrix class, copied from the source. Having matrices as columns in a tibble causes dplyr to throw errors, so a special method is needed to avoid copying the class attribute.

#### Value
A tibble constructed from the underlying matrix of the basis object. Each column will possess all
the attributes from the source object, except that the "class" attribute will be renamed to "basis.class"
to avoid interfering with dplyr operations.

#### Examples 
```{r}
library(splines)
library(tibble)
x <- seq(0, 1, by=0.001)
spl <- bs(x, df=6)
as_tibble(spl)
```
autoplot.aareg Autoplot survival::aareg

#### Description 
 
Autoplot survival::aareg

#### Usage 
<pre><code>
## S3 method for class 'aareg'
autoplot(object, maxtime = NULL, surv.connect = TRUE,
facets = TRUE, ncol = NULL, xlab = "", ylab = "", ...)
</code></pre>

#### Arguments 
 
* ``object``: survival::aareg instance
* ``maxtime``: truncate the input to the model at time "maxtime"
* ``surv.connect``: logical frag indicates whether connects survival curve to the origin
* ``facets``: Logical value to specify use facets
* ``ncol``: Number of facet/subplot columns
* ``xlab``: character vector or expression for x axis label
* ``ylab``: character vector or expression for y axis label
* ``...``: other arguments passed to autoplot.survfit

Value
ggplot

#### Examples 
```{r}
library(survival)
autoplot(aareg(Surv(time, status) ~ age + sex + ph.ecog, data = lung, nmin = 1))
```

autoplot.acf
Autoplot stats::acf. Note to pass ***plot = FALSE*** to original function to suppress standard plot output

#### Description 
 
Autoplot stats::acf. Note to pass ***plot = FALSE*** to original function to suppress standard plot
output

#### Usage 

<pre><code>
## S3 method for class 'acf'
autoplot(object, colour = "#000000", linetype = "solid",
conf.int = TRUE, conf.int.colour = "#0000FF", conf.int.linetype = "dashed", conf.int.fill = NULL,
conf.int.alpha = 0.3, conf.int.value = 0.95, conf.int.type = "white",
xlim = c(NA, NA), ylim = c(NA, NA), log = "", main = NULL, xlab = NULL, ylab = "ACF", asp = NULL, ...)
</code></pre>

#### Arguments 
 
* ``	object 	``: 	stats::acf instance
* ``	colour 	``: 	Line colour
* ``	linetype 	``: 	Line type
* ``	conf.int	``: 	Logical flag indicating whether to plot confidence intervals
* ``	conf.int.colour	``: 	line colour for confidence intervals
* ``	conf.int.linetype	``: 	line type for confidence intervals
* ``	conf.int.fill	``: 	fill colour for confidence intervals
* ``	conf.int.alpha 	``: 	alpha for confidence intervals
* ``	conf.int.value 	``: 	Coverage probability for confidence interval
* ``	conf.int.type 	``: 	Type of confidence interval, ***white*** for white noise or ***ma*** MA(k-1) model
* ``	xlim 	``: 	limits for x axis
* ``	ylim 	``: 	limits for y axis
* ``	log 	``: 	which variables to log transform ("x", "y", or "xy") main character vector or expression for plot title
* ``	xlab 	``: 	character vector or expression for x axis label
* ``	ylab 	``: 	character vector or expression for y axis label
* ``	asp	``: 	the y/x aspect ratio
* ``	... 	``: 	other arguments   passed to methods

Value
ggplot

#### Examples 
```{r}
autoplot(stats::acf(AirPassengers, plot = FALSE))
autoplot(stats::pacf(AirPassengers, plot = FALSE))
autoplot(stats::ccf(AirPassengers, AirPassengers, plot = FALSE))
```
