---
title: "ggfortify"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggfortify)
```

autoplot.stepfun

autoplot.varprd
Autoplot vars::varprd

#### Description 
 
Autoplot vars::varprd

#### Usage 
<pre><code>
## S3 method for class 'varprd'
autoplot(object, is.date = NULL, ts.connect = TRUE,
scales = "free_y", predict.geom = "line", predict.colour = "#0000FF",
predict.size = NULL, predict.linetype = NULL, predict.alpha = NULL,
predict.fill = NULL, predict.shape = NULL, conf.int = TRUE,
conf.int.colour = "#0000FF", conf.int.linetype = "none",
conf.int.fill = "#000000", conf.int.alpha = 0.3, ...)
</code></pre>

#### Arguments 
 
object vars::varpred instance
is.date Logical frag indicates whether the stats::ts is date or not. If not provided,
regard the input as date when the frequency is 4 or 12.
ts.connect Logical frag indicates whether connects original time-series and predicted val-
ues
scales Scale value passed to ggplot2cbind_wraps
predict.geom
35
geometric string for predicted time-series
* ``predict.colour``: line colour for predicted time-series
predict.size
point size for predicted time-series
predict.linetype
line type for predicted time-series
* ``predict.alpha``: alpha for predicted time-series
* ``predict.fill``: fill colour for predicted time-series
predict.shape point shape for predicted time-series
conf.int
Logical flag indicating whether to plot confidence intervals
conf.int.colour
line colour for confidence intervals
conf.int.linetype
line type for confidence intervals
conf.int.fill
fill colour for confidence intervals
* ``conf.int.alpha``: alpha for confidence intervals
...
* ``...``: other arguments passed to autoplot.ts
Value
ggplot

#### Examples 
```{r}
data(Canada, package = 'vars')
d.var <- vars::VAR(Canada, p = 3, type = 'const')
autoplot(stats::predict(d.var, n.ahead = 50), is.date = TRUE)
autoplot(stats::predict(d.var, n.ahead = 50), conf.int = FALSE)
```
cbind_wraps
Wrapper for cbind

#### Description 
 
Wrapper for cbind

#### Usage 
 <pre><code>
cbind_wraps(df1, df2)
</code></pre>
#### Arguments 
 
df1 1st data
df2 2nd data36
confint.acf
Value
list

#### Examples 
```{r}
ggfortify:::cbind_wraps(iris[1:2], iris[3:5])
```

check_names
Check data names are equal with expected

#### Description 
 
Check data names are equal with expected

#### Usage 
<pre><code>
check_names(data, expected)
</code></pre>

#### Arguments 
 
data list instance to be checked
expected expected character vector
Value
logical
confint.acf
Calcurate confidence interval for stats::acf

#### Description 
 
Calcurate confidence interval for stats::acf

#### Usage 
<pre><code>
## S3 method for class 'acf'
confint(x, ci = 0.95, ci.type = "white")
</code></pre>

#### Arguments 
 
* x stats::acf instance
* ci Float value for confidence interval
* ci.type "white" or "ma"

Value
vector

#### Examples 
```{r}
air.acf <- acf(AirPassengers, plot = FALSE)
ggfortify:::confint.acf(air.acf)
ggfortify:::confint.acf(air.acf, ci.type = 'ma')
```

deprecate.warning
Show deprecate warning

#### Description 
 
Show deprecate warning

#### Usage 
<pre><code>
deprecate.warning(old.kw, new.kw)
</code></pre>

#### Arguments 

* old.kw Keyword being deprecated
* ew.kw Keyword being replaced

#### Examples 
```{r}
ggfortify:::deprecate.warning('old', 'new')
```

fitted.ar
Calcurate fitted values for stats::ar

#### Description 
 
Calcurate fitted values for stats::ar

#### Usage 
<pre><code>
## S3 method for class 'ar'
fitted(object, ...)
</code></pre>

#### Arguments 
 
object stats::ar instance
... other keywords38
fortify.aareg
Value
ts An time series of the one-step forecasts

#### Examples 

fitted(ar(WWWUsage ))
flatten
Flatten dataframe contains matrix

#### Description 
 
tains list or matrix as column

#### Usage 
<pre><code>
flatten(df)
</code><pre>

#### Arguments 
 
df
fortify.aareg
data.frame to be flatten
Convert survival::aareg to data.frame

#### Description 
 
Convert survival::aareg to data.frame

#### Usage 
<pre><code>
## S3 method for class 'aareg'
fortify(model, data = NULL, maxtime = NULL,
surv.connect = TRUE, melt = FALSE, ...)
</code></pre>

#### Arguments 
 
* ``model``: survival::aareg instance
* ``data``: original dataset, if needed
* ``maxtime``: truncate the input to the model at time "maxtime"
* ``surv.connect``: logical frag indicates whether connects survival curve to the origin
* ``melt``: Logical flag indicating whether to melt each timeseries as variable
* ``... ``: other arguments passed to methods

Value
data.frame

#### Examples 
```{r}
library(survival)
fortify(aareg(Surv(time, status) ~ age + sex + ph.ecog, data = lung, nmin = 1))
fortify(aareg(Surv(time, status) ~ age + sex + ph.ecog, data = lung, nmin = 1), melt = TRUE)
```

fortify.acf
Convert stats::acf to data.frame

#### Description 
 
Convert stats::acf to data.frame

#### Usage 
<pre><code>
## S3 method for class 'acf'
fortify(model, data = NULL, conf.int = TRUE,
conf.int.value = 0.95, conf.int.type = "white", ...)
</code></pre>

#### Arguments 
 
* ``model``: stats::acf instance
* ``data``: original dataset, if needed
* ``conf.int``: Logical flag indicating whether to attach confidence intervals
* ``conf.int.value``: Coverage probability for confidence interval
* ``conf.int.type``: Type of confidence interval, ’white’ for white noise or ’ma’ MA(k-1) model
* ``... ``: other arguments passed to methods

Value
data.frame

#### Examples 
```{r}
fortify(stats::acf(AirPassengers))
fortify(stats::pacf(AirPassengers))
fortify(stats::ccf(AirPassengers, AirPassengers))
fortify(stats::acf(AirPassengers), conf.int = TRUE)

```
fortify.basis
Convert spline basis instances to data.frame

#### Description 
 
Convert spline basis instances to data.frame

#### Usage 
<pre><code>
## S3 method for class 'basis'
fortify(model, data, n = 256, ...)
</code></pre>

#### Arguments 
 
* ``model``: spline basis object
* ``data``: x-values at which to evaluate the splines. Optional. By default, an evenly spaced sequence of 256 values covering the range of the splines will be used.
* ``n``: If data is not provided, instead use an evenly-spaced sequence of x-values of this length (plus one, since both endpoints are included). If data is provided, this argument is ignored.
* ``... ``: other arguments passed to methods


Value
data.frame with 3 columns: Spline (character), x (numeric), and y (numeric); giving the interpolated
x and y values for each of the splines in the basis.

#### Examples 
```{r}
library(splines)
x <- seq(0, 1, by=0.001)
spl <- bs(x, df=6)
fortify(spl)

```


## fortify.cpt
Convert changepoint::cpt and strucchange::breakpoints to
data.frame

#### Description 
 
Convert changepoint::cpt and strucchange::breakpoints to data.frame

#### Usage 
<pre><code>
## S3 method for class 'cpt'
fortify(model, data = NULL, is.date = NULL, ...)
</code></pre>


#### Arguments 
 
* ``	model	``: 	chantepoint::cpt or strucchange::breakpoints instance
* ``	data	``: 	original dataset, if needed
* ``	is.date	``: 	Logical frag indicates whether the stats::ts is date or not. If not provided, regard the input as date when the frequency is 4 or 12.
* ``	...	``: 	other arguments   passed to methods

Value
data.frame

#### Examples 
```{r}
library(changepoint)
fortify(cpt.mean(AirPassengers))
fortify(cpt.var(AirPassengers))
fortify(cpt.meanvar(AirPassengers))
library(strucchange)
bp.nile <- breakpoints(Nile ~ 1)
fortify(bp.nile)
fortify(breakpoints(bp.nile, breaks = 2))
fortify(breakpoints(bp.nile, breaks = 2), data = Nile)
```

fortify.cv.glmnet
Convert glmnet::cv.glmnet to data.frame

#### Description 
 
Convert glmnet::cv.glmnet to data.frame

#### Usage 
<pre><code>
## S3 method for class 'cv.glmnet'
fortify(model, data = NULL, ...)
</code></pre>

#### Arguments 
 
* ``	model	``: 	glmnet::cv.glmnet instance
* ``	data	``: 	original dataset, if needed
* ``	...	``: 	other arguments passed to methods

Value
data.frame

#### Examples 
```{r}
fortify(glmnet::cv.glmnet(data.matrix(Orange[-3]), data.matrix(Orange[3])))42
fortify.dist
```

fortify.density
Convert stats::density to data.frame

#### Description 
 
Convert stats::density to data.frame

#### Usage 
<pre><code>
## S3 method for class 'density'
fortify(model, data = NULL, ...)
</code></pre>

#### Arguments 
 
* ``model``: stats::density instance
* ``data``: original dataset, if needed
* ``... ``: other arguments passed to methods
Value
data.frame

#### Examples 
```{r}
fortify(stats::density(stats::rnorm(1:50)))

```
fortify.dist
Convert stats::dist to data.frame

#### Description 
 
Convert stats::dist to data.frame

#### Usage 
<pre><code>
## S3 method for class 'dist'
fortify(model, data = NULL, ...)
</code></pre>

#### Arguments 
 
model stats::dist instance
data original dataset, if needed
* ``... ``: other arguments passed to methodsfortify.ets
43
Value
data.frame

#### Examples 
```{r}
fortify(eurodist)
```

fortify.ets
Convert forecast::bats and forecast::ets to data.frame

#### Description 
 
Convert forecast::bats and forecast::ets to data.frame

#### Usage 
<pre><code>
## S3 method for class 'ets'
fortify(model, data = NULL, ...)
</code></pre>

#### Arguments 
 
* model forecast::bats or forecast::ets instance
* data original dataset, if needed
* ``... ``: other arguments passed to methods
Value
data.frame

#### Examples 
```{r}
## Not run:
fortify(forecast::bats(UKgas))
fortify(forecast::ets(UKgas))
## End(Not run)44

```

fortify.forecast
fortify.factanal
Convert stats::factanal to data.frame

#### Description 
 
Convert stats::factanal to data.frame

#### Usage 
 <pre><code>
## S3 method for class 'factanal'
fortify(model, data = NULL, ...)

#### Arguments 
 
model stats::factanal instance
data original dataset, if needed
* ``... ``: other arguments passed to methods
Value
data.frame

#### Examples 
```{r}
d.factanal <- stats::factanal(state.x77, factors = 3, scores = 'regression')
fortify(d.factanal)
fortify(d.factanal, data = state.x77)
```

fortify.forecast
Convert forecast::forecast to data.frame

#### Description 
 
Convert forecast::forecast to data.frame

#### Usage 
<pre><code>
## S3 method for class 'forecast'
fortify(model, data = NULL, is.date = NULL,
ts.connect = FALSE, ...)
</code></pre>

#### Arguments 
 
* ``model``: forecast::forecast instance
* ``data``: original dataset, if needed
* ``is.date``: Logical frag indicates whether the stats::ts is date or not. If not provided,
regard the input as date when the frequency is 4 or 12.
* ``ts.connect Logical frag indicates whether connects original time-series and predicted val-
ues
* ``... ``: other arguments passed to methods
Value
data.frame

#### Examples 
```{r}
d.arima <- forecast::auto.arima(AirPassengers)
d.forecast <- forecast::forecast(d.arima, level = c(95), h = 50)
fortify(d.forecast)
fortify(d.forecast, ts.connect = TRUE)
```
