### Sample data set
In order to create a Sankey diagram in ggplot2 you will need to install the ggsankey library and transform your dataset using the make_long function from the package. 
The columns of the data must represent x (the current stage), next_x (the following stage), node (the current node) and next_node (the following node). Note that the last stage should point to an NA.

```{r}
install.packages("remotes")
library(remotes)
```

```{r}
remotes::install_github("davidsjoberg/ggsankey")
library(ggsankey)

df <- mtcars %>%
  make_long(cyl, vs, am, gear, carb) 
``` 

### dataset

```{r}
head(df)

```


### Node, flow and stage of ggsankey

Sankey plot with ggsankey
The ggsankey package contains a geom named geom_sankey to create the Sankey diagrams in ggplot2. Note that you will need to pass the variables to aes, specifying a factor as the fill color. The function also contains a theme named theme_sankey.



```{r}
 
# install.packages("remotes")
# remotes::install_github("davidsjoberg/ggsankey")
library(ggsankey)
# install.packages("ggplot2")
library(ggplot2)
# install.packages("dplyr")
library(dplyr) # Also needed

ggplot(df, aes(x = x, 
               next_x = next_x, 
               node = node, 
               next_node = next_node,
               fill = factor(node))) +
  geom_sankey() +
  theme_sankey(base_size = 16) 
 
``` 

### plot

 
Sankey diagram in ggplot2
```{r}
p

```
 
 
 
 
 



### Adding labels

You can also add labels to the Sankey diagram using the geom_sankey_label function of the package. Recall to specify the label inside aes as the variable you want to show.

# install.packages("remotes")
# remotes::install_github("davidsjoberg/ggsankey")
library(ggsankey)
# install.packages("ggplot2")
library(ggplot2)
# install.packages("dplyr")
library(dplyr) # Also needed

ggplot(df, aes(x = x, 
               next_x = next_x, 
               node = node, 
               next_node = next_node,
               fill = factor(node),
               label = node)) +
  geom_sankey() +
  geom_sankey_label() +
  theme_sankey(base_size = 16) 
``` 

### plot

```{r}
p

```
 
### Sankey diagram in ggplot2 with labels

Color customization
There are several arguments that can be customized to change the appearance of the Sankey diagram in R. The following images were created by the author of the package to serve as reference:

geom_sankey aesthetics

geom_sankey geometries

Color and fill of the Sankey plot

As an example, modifying some arguments of the geom_sankey function and changing the fill color palette we can create something like the following:

Sankey diagram in R with ggsankey

# install.packages("remotes")
# remotes::install_github("davidsjoberg/ggsankey")
library(ggsankey)
# install.packages("ggplot2")
library(ggplot2)
# install.packages("dplyr")
library(dplyr) # Also needed

ggplot(df, aes(x = x, 
               next_x = next_x, 
               node = node, 
               next_node = next_node,
               fill = factor(node))) +
  geom_sankey(flow.alpha = 0.75, node.color = 1) +
  scale_fill_viridis_d(option = "A", alpha = 0.95) +
  theme_sankey(base_size = 16) 
``` 

### plot

```{r}
p

```
 
Changing the color of the labels

Note that the geom_sankey_label also contains several arguments to change the appearance of the labels of the plot.

Customizing a Sankey diagram in ggplot2 with ggsankey package

# install.packages("remotes")
# remotes::install_github("davidsjoberg/ggsankey")
library(ggsankey)
# install.packages("ggplot2")
library(ggplot2)
# install.packages("dplyr")
library(dplyr) # Also needed

ggplot(df, aes(x = x, 
               next_x = next_x, 
               node = node, 
               next_node = next_node,
               fill = factor(node),
               label = node)) +
  geom_sankey(flow.alpha = 0.5, node.color = 1) +
  geom_sankey_label(size = 3.5, color = 1, fill = "white") +
  scale_fill_viridis_d(option = "A", alpha = 0.95) +
  theme_sankey(base_size = 16) 
``` 

### plot

```{r}
p

```

  
Legend customization

### Changing the title of the legend

As with other ggplot2 charts it is possible to change the title of the legend. In this case you can do the following:


```{r}
# install.packages("remotes")
# remotes::install_github("davidsjoberg/ggsankey")
library(ggsankey)
# install.packages("ggplot2")
library(ggplot2)
# install.packages("dplyr")
library(dplyr) # Also needed

p <- ggplot(df, aes(x = x, 
               next_x = next_x, 
               node = node, 
               next_node = next_node,
               fill = factor(node),
               label = node)) +
  geom_sankey(flow.alpha = 0.5, node.color = 1) +
  geom_sankey_label(size = 3.5, color = 1, fill = "white") +
  scale_fill_viridis_d() +
  theme_sankey(base_size = 16) +
  guides(fill = guide_legend(title = "Title")) 
``` 

### Sankey plot in R

```{r}
p

```



### Removing the legend

Finally, if you want to get rid of the legend of the Sankey plot you can set its position to "none".


 
# install.packages("remotes")
# remotes::install_github("davidsjoberg/ggsankey")
library(ggsankey)
# install.packages("ggplot2")
library(ggplot2)
# install.packages("dplyr")
library(dplyr) # Also needed

ggplot(df, aes(x = x, 
               next_x = next_x, 
               node = node, 
               next_node = next_node,
               fill = factor(node),
               label = node)) +
  geom_sankey(flow.alpha = 0.5, node.color = 1) +
  geom_sankey_label(size = 3.5, color = 1, fill = "white") +
  scale_fill_viridis_d() +
  theme_sankey(base_size = 16) +
  theme(legend.position = "none") 
Remove the legend of a Sankey diagram in ggplot2


ggplot2
ggplot2

Elegant Graphics for Data Analysis

BUY ON AMAZON
