---
title: "Sankey Plot with plotly"
output: flexdashboard::flex_dashboard
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(plotly)

library(ggplot2)
library(tidyverse)
```

Basic Sankey Diagram
=============================================

Column {.tabset}
------------------------

### Basic Sankey Diagram - Code

```{r}
fig <- plot_ly(
    type = "sankey",
    orientation = "h",

    node = list(
      label = c("A1", "A2", "B1", "B2", "C1", "C2"),
      color = c("blue", "blue", "blue", "blue", "blue", "blue"),
      pad = 15,
      thickness = 20,
      line = list(
        color = "black",
        width = 0.5
      )
    ),

    link = list(
      source = c(0,1,0,2,3,3),
      target = c(2,3,3,4,4,5),
      value =  c(8,4,2,8,4,2)
    )
  )
fig <- fig %>% layout(
    title = "Basic Sankey Diagram",
    font = list(
      size = 10
    )
)


```

### Basic Sankey Diagram - Plot

```{r}


fig
```


Creating a Canvas
=========================================

Column {.tabset}
----------------------------

### Create Canvas - Code


```{r}
#library(plotly)

fig <- plot_ly(
    type = "sankey",
    domain = list(
      x =  c(0,1),
      y =  c(0,1)
    ),
    orientation = "h",
    valueformat = ".0f",
    valuesuffix = "TWh"
)

```


### DECC Energy Forecast - Code 

```{r}

fig <- fig %>% layout(
    title = "Energy forecast for 2050, UK - Department of Energy & Climate Change",
    font = list(
      size = 10
    ),
    xaxis = list(showgrid = F, zeroline = F),
    yaxis = list(showgrid = F, zeroline = F)
  )


```


### Adding Nodes


```{r}

# library(plotly)
library(rjson)

json_file <- "https://raw.githubusercontent.com/plotly/plotly.js/master/test/image/mocks/sankey_energy.json"
json_data <- fromJSON(paste(readLines(json_file), collapse=""))

fig <- plot_ly(
    type = "sankey",
    domain = list(
      x =  c(0,1),
      y =  c(0,1)
    ),
    orientation = "h",
    valueformat = ".0f",
    valuesuffix = "TWh",

    node = list(
      label = json_data$data[[1]]$node$label,
      color = json_data$data[[1]]$node$color,
      pad = 15,
      thickness = 15,
      line = list(
        color = "black",
        width = 0.5
      )
    )
  ) 

```

### Finishing Touchs 

```{r}

fig <- fig %>% layout(
    title = "Energy forecast for 2050, UK - Department of Energy & Climate Change",
    font = list(
      size = 10
    ),
    xaxis = list(showgrid = F, zeroline = F),
    yaxis = list(showgrid = F, zeroline = F)
)

fig
```



### Add Links

```{r}
library(plotly)
library(rjson)

json_file <- "https://raw.githubusercontent.com/plotly/plotly.js/master/test/image/mocks/sankey_energy.json"
json_data <- fromJSON(paste(readLines(json_file), collapse=""))

fig <- plot_ly(
    type = "sankey",
    domain = list(
      x =  c(0,1),
      y =  c(0,1)
    ),
    orientation = "h",
    valueformat = ".0f",
    valuesuffix = "TWh",

    node = list(
      label = json_data$data[[1]]$node$label,
      color = json_data$data[[1]]$node$color,
      pad = 15,
      thickness = 15,
      line = list(
        color = "black",
        width = 0.5
      )
    ),

    link = list(
      source = json_data$data[[1]]$link$source,
      target = json_data$data[[1]]$link$target,
      value =  json_data$data[[1]]$link$value,
      label =  json_data$data[[1]]$link$label
    )
  ) 
fig <- fig %>% layout(
    title = "Energy forecast for 2050<br>Source: Department of Energy & Climate Change, Tom Counsell via <a href='https://bost.ocks.org/mike/sankey/'>Mike Bostock</a>",
    font = list(
      size = 10
    ),
    xaxis = list(showgrid = F, zeroline = F),
    yaxis = list(showgrid = F, zeroline = F)
)

```


### Plot

```{r}
fig
```


Style Sankey Diagram
=======================================

Column {.tabset}
---------------------------------------------------------

### Style Sankey Diagram


```{r}
library(plotly)
library(rjson)

json_file <- "https://raw.githubusercontent.com/plotly/plotly.js/master/test/image/mocks/sankey_energy_dark.json"
json_data <- fromJSON(paste(readLines(json_file), collapse=""))

fig <- plot_ly(
    type = "sankey",
    domain = list(
      x =  c(0,1),
      y =  c(0,1)
    ),
    orientation = "h",
    valueformat = ".0f",
    valuesuffix = "TWh",

    node = list(
      label = json_data$data[[1]]$node$label,
      color = json_data$data[[1]]$node$color,
      pad = 15,
      thickness = 15,
      line = list(
        color = "black",
        width = 0.5
      )
    ),

    link = list(
      source = json_data$data[[1]]$link$source,
      target = json_data$data[[1]]$link$target,
      value =  json_data$data[[1]]$link$value,
      label =  json_data$data[[1]]$link$label
    )
  )

```

### DECC Data

```{r}

fig <- fig %>% layout(
    title = "Energy forecast for 2050<br>Source: Department of Energy & Climate Change, Tom Counsell via <a href='https://bost.ocks.org/mike/sankey/'>Mike Bostock</a>",
    font = list(
      size = 10,
      color = 'white'
    ),
    xaxis = list(showgrid = F, zeroline = F, showticklabels = F),
    yaxis = list(showgrid = F, zeroline = F, showticklabels = F),
    plot_bgcolor = 'black',
    paper_bgcolor = 'black'
)


```

### Plot

```{r}
fig
```


Node Positioning
=======================

### Define Node Position


The following example sets node.x and node.y to place nodes in the specified locations, except in the snap arrangement (default behaviour when node.x and node.y are not defined) to avoid overlapping of the nodes, therefore, an automatic snapping of elements will be set to define the padding between nodes via nodepad. The other possible arrangements are: 1) perpendicular 2) freeform 3) fixed

```{r}


library(plotly)
fig <- plot_ly(
  type = "sankey",
  arrangement = "snap",
  node = list(
    label = c("A", "B", "C", "D", "E", "F"),
    x = c(0.2, 0.1, 0.5, 0.7, 0.3, 0.5),
    y = c(0.7, 0.5, 0.2, 0.4, 0.2, 0.3),
    pad = 10), # 10 Pixel
  link = list(
    source = c(0, 0, 1, 2, 5, 4, 3, 5),
    target = c(5, 3, 4, 3, 0, 2, 2, 3),
    value = c(1, 2, 1, 1, 1, 1, 1, 2)))
fig <- fig %>% layout(title = "Sankey with manually positioned node")

fig
```


### Reference
See https://plotly.com/r/reference/#sankey for more information and options!